\large A new global measure of environmental unpredictability

### 2025-04-14 writing/appendix-A.Rmd
re-arranged appendix figs based on refs in text

\noindent Figure A1 below illustrates the color palettes used in this appendix, for each type of vision (trichromatic, deuteranope, protanope, tritanope, and achomatic). Palette A was created by Masataka Okabe and Kei Ito [@okabe_color_2008], while the other palettes were created by Fabio Crameri [@crameri_geodynamic_2018; @crameri_scientific_2018]. All palettes below are available via the `khroma` package [@frerebeau_khroma_2024] for `R` [@r_core_team_r_2024]. Figures A2-A5 show some of the data used for fitting the models for estimating mean NDVI and the variance around the mean. The code for generating the figures is available [on GitHub](https://github.com/QuantitativeEcologyLab/ndvi-stochasticity/blob/main/analysis/figures/input-data.R).

>>>>

\noindent Figure A1 below illustrates the color palettes used in this appendix, for each type of vision (trichromatic, deuteranope, protanope, tritanope, and achomatic). Palette A4 was created by Masataka Okabe and Kei Ito [@okabe_color_2008], while the other palettes were created by Fabio Crameri [@crameri_geodynamic_2018; @crameri_scientific_2018]. All palettes below are available via the `khroma` package [@frerebeau_khroma_2024] for `R` [@r_core_team_r_2024]. Figures A2-A5 show some of the data used for fitting the models for estimating mean NDVI and the variance around the mean. The code for generating the figures is available on GitHub at [https://github.com/QuantitativeEcologyLab/ndvi-stochasticity/blob/main/analysis/figures/input-data.R](https://github.com/QuantitativeEcologyLab/ndvi-stochasticity/blob/main/analysis/figures/input-data.R).
